---
title: "IE451_HW1_YigitAliKaradogan"
format: html
editor: visual
---

## HW1

Upload required packages

```{r}
library("nycflights13")
library("tidyverse")
```

## Question-1

Take a look at 'flights' data

```{r}
flights
```

**5.2.4 - 1.1** Find all flights that had an arrival delay of two or more hours

```{r}
flights %>% filter(arr_delay >= 120)
```

**5.2.4 - 1.2** Find all flights that flew to Houston (`IAH` or `HOU`)

```{r}
flights %>% filter(dest=='IAH' | dest=='HOU')
```

**5.2.4 - 1.3** Find all flights that were operated by United, American, or Delta

```{r}
airlines
flights %>% filter(carrier %in% c('UA','AA','DL'))
```

**5.2.4 - 1.4** Find all flights that departed in summer (July, August, and September)

```{r}
flights %>% filter(month %in% c(7:9))
```

**5.2.4 - 1.5** Find all flights that arrived more than two hours late, but didn't leave late

```{r}
flights %>% filter(arr_delay > 120, dep_delay <= 0)
```

**5.2.4 - 1.6** Find all flights that were delayed by at least an hour, but made up over 30 minutes in flight

```{r}
flights %>% filter(dep_delay >= 60, dep_delay - arr_delay > 30)
```

**5.2.4 - 1.7** Find all flights that departed between midnight and 6am (inclusive)

```{r}
flights %>% filter(dep_time <= 600 | dep_time == 2400)
```

**5.2.4 - 2 A**nother useful dplyr filtering helper is between(). What does it do? Can you use it to simplify the code needed to answer the previous challenges?

between() is used to check that whether a numeric value falls in a specific range or not. I can do it for **5.2.4 - 1.4** as follows:

```{r}
flights %>% filter(between(month, 7, 9))
```

**5.2.4 - 3 H**ow many flights have a missing `dep_time`? What other variables are missing? What might these rows represent?

```{r}
flights %>% filter(is.na(dep_time))
```

dep_delay, arr_time, arr_delay, air_time are also missing. These may be cancelled flights.

**5.3.1 - 2 S**ort `flights` to find the most delayed flights. Find the flights that left earliest.

```{r}
flights %>% arrange(desc(dep_delay))
```

```{r}
flights %>% arrange(dep_delay)
```

B6 97 JFK to DEN was the flight that left the airport earliest.

**5.3.1 - 3** Sort `flights` to find the fastest (highest speed) flights.

```{r}
flights %>% arrange(desc(distance/air_time))
```

DL 1499 is the fastest flight

**5.3.1 - 4** Which flights travelled the farthest? Which travelled the shortest?

```{r}
flights %>% arrange(desc(distance))
```

HA 51 traveled the farthest

```{r}
flights %>% arrange(distance)
```

US 1631 traveled the shortest

**5.6.7 - 5** Which carrier has the worst delays? Challenge: can you disentangle the effects of bad airports vs. bad carriers? Why/why not? (Hint: think about `flights %>% group_by(carrier, dest) %>% summarise(n())`)

```{r}
flights %>%
  group_by(carrier) %>%
  summarise(arr_delay = mean(arr_delay, na.rm = TRUE)) %>%
  arrange(desc(arr_delay))
```

F9 - Frontier Airlines has the worst delays

**5.7.1 - 2** Which plane (`tailnum`) has the worst on-time record?

```{r}
flights %>%
  filter(!is.na(arr_delay)) %>%
  group_by(tailnum) %>%
  summarise(arr_delay = mean(arr_delay)) %>% 
  arrange(desc(arr_delay))
```

N844MH has the worst on-time record since it has the most delays

**5.7.1 - 3** What time of day should you fly if you want to avoid delays as much as possible?

```{r}
flights %>%
  group_by(hour) %>%
  summarise(arr_delay = mean(arr_delay, na.rm = TRUE)) %>%
  arrange(arr_delay)
```

7AM has the fewest delays
